Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-15 scagnostics.Rmd
section 3 re-organisation

- Compare the index values for structured vs nuisance variables, by simulating many examples from the model families, and recording the 90% confidence intervals. This checks if the PPI can detect the structure, that it has distinct differences between the sets of values. 
- Use the tour to show the index values along an interpolation between pairs of nuisance variables, $x_1 - x_2$ view either to the $x_3 - x_4$. The result is ideally a smooth change in low values. This checks the smoothness property. 
- Use the tour to show the index values along an interpolation between a pair of nuisance variables $x_1 - x_2$ and the structured pair of variables $x_5 - x_6$. This examines the squintability, and smoothness. If the function is smooth and slowly increases towards the structured projection, then the structure is visible from a distance. 
- A guided tour, showing the optimisation path, starting from $x_1 - x_2$, for one index, shows how effectively the maximum is attained. The values for other PPIs is computed for this path also, which allows an assessment of similarity between PPIs. 
- Rotation invariance is checked by computing PPIs on rotations of the structured projection. 
- Benchmarking is used to assess the computational speed.

@@

## Index function parameters
\label{sec:params}
Some parameters must be fixed when using the index functions considered here, controlling trade-offs between noise and fine structure detection, and between computing time and precision.

## Guided tour
\label{sec:guided}

@@

>>>>

- Compare the index values for structured vs nuisance variables, by simulating many examples from the model families, and recording the 90% confidence intervals. This checks if the PPI can detect the structure, that it has distinct differences between the sets of values. 
- Use the tour to show the index values along an interpolation between pairs of nuisance variables, $x_1 - x_2$ view either to the $x_3 - x_4$. The result is ideally a smooth change in low values. This checks the smoothness property. 
- Use the tour to show the index values along an interpolation between a pair of nuisance variables $x_1 - x_2$ and the structured pair of variables $x_5 - x_6$. This examines the squintability, and smoothness. If the function is smooth and slowly increases towards the structured projection, then the structure is visible from a distance. 
- Ease of optimisation depends on having a smooth function, and this is tested using a guided tour, showing the optimisation path, starting from $x_1 - x_2$.  One index is optimised to show how effectively the maximum is attained, and the values for other PPIs is examined along the same path, which allows an assessment of similarity between PPIs. 
- Rotation invariance is checked by computing PPIs on rotations of the structured projection. 
- Varying the parameters for PPIs is used to examine the effect on value, smoothness, how flexible the index can be to find different structure and whether the index is fiddly to tune. Trace plots between noise and structured projections are used to examine this. 
- Benchmarking on a range of sample sizes is used to assess the computational speed.

@@

## Ease of optimisation
\label{sec:guided}

- remind reader of the options for optimisation in guided tour
- how you use them here
-

The guided tour combines optimisation with interpolating between pairs of planes. Target planes of the path are chosen by a random search method to find projection planes with high index values, which are then interpolated between. It operates roughly like simulated annealing that as one gets closer to an optimal value the random search range is reduced.

@@

## Effect of parameter choice in nndex value
\label{sec:params}
Some parameters must be fixed when using the index functions considered here, controlling trade-offs between noise and fine structure detection, and between computing time and precision.
